---
title: "R package investigation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R package investigation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


### Setup environment  
```{r setup}
library(AusCropSuitR)
```

## Preface  

This document is a wandering guide to other ecological models writen in R and 
available predominantly on github or referenced by [EcoCommons](https://www.ecocommons.org.au/).
Many of these packages were also found via [R-universe](https://r-universe.dev/search).  

## dismo  

This package is the R implementation of BioClim and contains extra features.
Educational material on this package can be found at the following locations.  

 Github: https://github.com/rspatial/dismo  
 EcoCommons: https://support.ecocommons.org.au/support/solutions/articles/6000254285-bioclim  
 r-universe: https://rspatial.r-universe.dev/dismo  
 
```{r dismo-install}
install.packages('dismo', repos='https://rspatial.r-universe.dev')
library(dismo)
```

```{r}
logo <- stack(system.file("external/rlogo.grd", package="raster"))
#presence data
pts <- matrix(c(48.243420, 48.243420, 47.985820, 52.880230, 49.531423, 46.182616, 54.168232, 
  69.624263, 83.792291, 85.337894, 74.261072, 83.792291, 95.126713, 84.565092, 66.275456, 41.803408,
  25.832176, 3.936132, 18.876962, 17.331359,7.048974, 13.648543, 26.093446, 28.544714, 39.104026, 
  44.572240, 51.171810, 56.262906, 46.269272, 38.161230, 30.618865, 21.945145, 34.390047, 59.656971,
  69.839163, 73.233228, 63.239594, 45.892154, 43.252326, 28.356155) , ncol=2)
bc <- bioclim(logo, pts)

#or
v <- extract(logo, pts)
bc <- bioclim(v)
p1 <- predict(logo, bc)
p2 <- predict(logo, bc, tails=c('both', 'low', 'high'))

#or
#sp <- SpatialPoints(pts)
#bc <- bioclim(logo, pts)

plot(p1)
plot(p2)
vignette('sdm', 'dismo')
```
 

```{r}
library(jsonlite)
library(httr)
#library(htmltidy)
library(XML)
library(xml2)
#devtools::install_github("hrbrmstr/jsonview")
library(jsonview)


# Get the raw json from the Providers endpoint
rawJson <- content(GET('https://esoil.io/TERNLandscapes/SoilDataFederatoR/SoilDataAPI/DataSets'), "text")

# View the raw json data
json_view(rawJson)
json_tree_view(rawJson)

# Get the raw json from the Providers endpoint and create a dataframe - This is probably the best way to use the SoilDataFederator endpoint in R
df <- fromJSON('https://esoil.io/TERNLandscapes/SoilDataFederatoR/SoilDataAPI/DataSets')
head(df)

# Get the Providers data as XML
rawXML <- content(GET('https://esoil.io/TERNLandscapes/SoilDataFederatoR/SoilDataAPI/DataSets?format=xml'), "text")

xml_view(rawXML)

# Get the Providers data as XML and create a dataframe
doc<-xmlParse(rawXML)
xmldf <- xmlToDataFrame(nodes = getNodeSet(doc, "//DataSetsRecord"))
head(xmldf)

# Get the Providers data as a CSV file
csvf <- tempfile()
download.file('https://esoil.io/TERNLandscapes/SoilDataFederatoR/SoilDataAPI/DataSets?format=csv', csvf, mode="wb", quiet = T)
df <- read.csv(csvf)
head(df)
unlink(csvf)




# get the soil property groups from the PropertyGroups endpoint
url <- 'https://esoil.io/TERNLandscapes/SoilDataFederatoR/SoilDataAPI/Properties'
df <- fromJSON(url)
head(df, 20)



# get the soil property groups from the PropertyGroups endpoint
url <- 'https://esoil.io/TERNLandscapes/SoilDataFederatoR/SoilDataAPI/PropertyGroups'
df <- fromJSON(url)
head(df)




# get the soil property data from the SoilData endpoint
url <- 'https://esoil.io/TERNLandscapes/SoilDataFederatoR/SoilDataAPI/SoilData?observedProperty=3A1&DataSet=TasGovernment'
df <- fromJSON(url)
head(df)
```




