---
title: "R package investigation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R package investigation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


### Setup environment  
```{r setup}
library(AusCropSuitR)
```

## Preface  

This document is a wandering guide to other ecological models writen in R and 
available predominantly on github or referenced by [EcoCommons](https://www.ecocommons.org.au/).
Many of these packages were also found via [R-universe](https://r-universe.dev/search).  

## dismo  

This package is the R implementation of BioClim and contains extra features.
Educational material on this package can be found at the following locations.  

 Github: https://github.com/rspatial/dismo  
 EcoCommons: https://support.ecocommons.org.au/support/solutions/articles/6000254285-bioclim  
 r-universe: https://rspatial.r-universe.dev/dismo  
 

 
